Beam-Helicity and Beam-Charge Asymmetries\\ Associated with Deeply Virtual Compton Scattering\\ on the Unpolarised Proton \underline{Paper Tag: PDVCS0607 (v3.0)} \underline{Drafting Committee: DC90 (\today)}

### 2012-02-09 paper.tex
paper prepared for submission to g. schnell

\documentclass[11pt,a4paper]{article}
\usepackage{jheppub}
\pdfoutput=1
\toccontinuoustrue
\usepackage{lscape}
\usepackage{vruler}
\usepackage{subfigure}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{appendix}
%\usepackage[section]{placeins}

@@

% List of Institute Addresses 
\collaboration{The {\sc Hermes} Collaboration}

@@

Generalised parton distributions depend upon four kinematic variables: the
Mandelstam variable $t=(p-p^{\prime})^2$, which is the squared momentum
transfer to the target nucleon in the exclusive scattering process with $p$ ($p^{\prime}$)
representing the initial (final) four-momentum of the nucleon; the average
fraction $x$ of the nucleon's longitudinal momentum carried by the active
quark throughout the scattering process; half the difference of
  the fractions of the nucleon's longitudinal momentum carried
by the active quark at the start and end of the process, written as
the skewness $\xi$; and $Q^2=-(q^2)$, i.e. the negative square of the four-momentum of
the virtual photon that mediates the lepton-nucleon scattering
process. In the Bjorken limit of $Q^2\rightarrow\infty$ with fixed
$t$, the skewness $\xi$ is related to the Bjorken variable
$x_{\textrm{B}}=\frac{-q^2}{2p\cdot q}$ as
$\xi\approx\frac{x_\textrm{B}}{2-x_\textrm{B}}$. The results are presented
as a function of $x_{\textrm{B}}$ because there is no consensus on an experimentally observable representation of $\xi$. 
Exclusive leptoproduction of real photons
 arises from
two experimentally indistinguishable processes: the Deeply Virtual Compton Scattering (DVCS) process,
which is the emission of a real photon by the struck quark from the nucleon, and the Bethe--Heitler (BH) process, which is elastic lepton-nucleon scattering with the emission of a bremsstrahlung photon by the lepton.
\begin{figure}
\begin{center}
\subfigure[DVCS]{\includegraphics[angle=90,width=0.45\textwidth]{dvcs_both_edited}}
\subfigure[Bethe-Heitler]{\includegraphics[angle=90,width=0.45\textwidth]{bh_both_edited}}
\caption[DVCS and Bethe Heitler hand bag diagram.]{(a): The leading DVCS process in which an electron/positron ($e$) interacts with a quark in the nucleon
($N$) via a virtual photon ($\gamma^\ast$). The quark is found in the
nucleon with longitudinal momentum fraction $x+\xi$ and emits a real
photon ($\gamma$). The quark is absorbed by the nucleon with
longitudinal momentum fraction $x-\xi$. (b): The leading Bethe-Heitler process, i.e. the emission of a real photon from the incoming or outgoing lepton. This process has the same initial and final states as DVCS.}
\label{spin}
\end{center}
\end{figure}
The BH process is calculable in the QED framework; this process is
dominant at the kinematic conditions of the H{\sc ermes} experiment. The
two processes interfere and the large BH amplitude
amplifies the interference term, which is proportional to the DVCS amplitude. It is through the study of this interference term that useful information for the constraint of certain GPDs can be obtained at H{\sc ermes} kinematic conditions, especially since the interference term is the only part of the squared scattering amplitude that is linear in CFFs~\cite{Bel02b}.

@@

\begin{align}
\mathcal{A}^{\textrm{DVCS}}_{\textrm{LU}}(\phi) &\equiv
\frac{(\textrm{d}\sigma(\phi)^{+\rightarrow} +
\textrm{d}\sigma(\phi)^{-\rightarrow}) -
(\textrm{d}\sigma(\phi)^{+\leftarrow} + 
\textrm{d}\sigma(\phi)^{-\leftarrow})}
{(\textrm{d}\sigma(\phi)^{+\rightarrow} +
\textrm{d}\sigma(\phi)^{-\rightarrow}) +
(\textrm{d}\sigma(\phi)^{+\leftarrow}
+ \textrm{d}\sigma(\phi)^{-\leftarrow})}& \nonumber \\[0.4cm]
%\\ \nonumber
&=\dfrac{ K_{\textrm{DVCS}} s_{\textrm{unp},1}^{\textrm{DVCS}}\sin\phi}{\dfrac{K_{\textrm{BH}}}{\mathcal{P}_{1}
(\phi)\mathcal{P}_{2}(\phi)}
\displaystyle\sum_{n=0}^2
c_{\textrm{unp},n}^{\textrm{BH}}\cos(n\phi) + 
K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2
c_{\textrm{unp},n}^{\textrm{DVCS}}\cos(n\phi)}\, , &
\label{e:aludvcs}
\end{align}

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage{jheppub}
\pdfoutput=1
\toccontinuoustrue
\usepackage{lscape}
%\usepackage{vruler}
\usepackage{subfigure}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{appendix}

@@

\collaboration{The {\sc Hermes} Collaboration}

@@

Generalised parton distributions depend upon four kinematic variables: the
Mandelstam variable $t=(p-p^{\prime})^2$, which is the squared momentum
transfer to the target nucleon in the exclusive scattering process with $p$ ($p^{\prime}$)
representing the initial (final) four-momentum of the nucleon; the average
fraction $x$ of the nucleon's longitudinal momentum carried by the active
quark throughout the scattering process; half the difference of
  the fractions of the nucleon's longitudinal momentum carried
by the active quark at the start and end of the process, written as
the skewness $\xi$; and $Q^2=-(q^2)$, i.e. the negative square of the four-momentum of
the virtual photon that mediates the lepton-nucleon scattering
process. In the Bjorken limit of $Q^2\rightarrow\infty$ with fixed
$t$, the skewness $\xi$ is related to the Bjorken variable
$x_{\textrm{B}}=\frac{-q^2}{2p\cdot q}$ as
$\xi\approx\frac{x_\textrm{B}}{2-x_\textrm{B}}$. The results are presented
as a function of $x_{\textrm{B}}$ because there is no consensus on an experimentally observable representation of $\xi$. 
Exclusive leptoproduction of real photons
 arises from
two experimentally indistinguishable processes: the Deeply Virtual Compton Scattering (DVCS) process,
which is the emission of a real photon by the struck quark from the nucleon, and the Bethe--Heitler (BH) process, which is elastic lepton-nucleon scattering with the emission of a bremsstrahlung photon by the lepton.
\begin{figure}
\begin{center}
\subfigure[DVCS]{\includegraphics[angle=90,width=0.48\textwidth]{dvcs_both_edited}}
\subfigure[Bethe-Heitler]{\includegraphics[angle=90,width=0.48\textwidth]{bh_both_edited}}
\caption[DVCS and Bethe Heitler hand bag diagram.]{(a): The leading DVCS process in which an electron/positron ($e$) interacts with a quark in the nucleon
($N$) via a virtual photon ($\gamma^\ast$). The quark is found in the
nucleon with longitudinal momentum fraction $x+\xi$ and emits a real
photon ($\gamma$). The quark is absorbed by the nucleon with
longitudinal momentum fraction $x-\xi$. (b): The leading Bethe-Heitler process, i.e. the emission of a real photon from the incoming or outgoing lepton. This process has the same initial and final states as DVCS.}
\label{spin}
\end{center}
\end{figure}
The BH process is calculable in the QED framework; this process is
dominant at the kinematic conditions of the H{\sc ermes} experiment. The
two processes interfere and the large BH amplitude
amplifies the interference term, which is proportional to the DVCS amplitude. It is through the study of this interference term that useful information for the constraint of certain GPDs can be obtained at H{\sc ermes} kinematic conditions, especially since the interference term is the only part of the squared scattering amplitude that is linear in CFFs~\cite{Bel02b}.

@@

\begin{align}
\mathcal{A}^{\textrm{DVCS}}_{\textrm{LU}}(\phi) &\equiv
\frac{(\textrm{d}\sigma(\phi)^{+\rightarrow} +
\textrm{d}\sigma(\phi)^{-\rightarrow}) -
(\textrm{d}\sigma(\phi)^{+\leftarrow} + 
\textrm{d}\sigma(\phi)^{-\leftarrow})}
{(\textrm{d}\sigma(\phi)^{+\rightarrow} +
\textrm{d}\sigma(\phi)^{-\rightarrow}) +
(\textrm{d}\sigma(\phi)^{+\leftarrow}
+ \textrm{d}\sigma(\phi)^{-\leftarrow})}& \nonumber \\[0.4cm]
&=\dfrac{ K_{\textrm{DVCS}} s_{\textrm{unp},1}^{\textrm{DVCS}}\sin\phi}{\dfrac{K_{\textrm{BH}}}{\mathcal{P}_{1}
(\phi)\mathcal{P}_{2}(\phi)}
\displaystyle\sum_{n=0}^2
c_{\textrm{unp},n}^{\textrm{BH}}\cos(n\phi) + 
K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2
c_{\textrm{unp},n}^{\textrm{DVCS}}\cos(n\phi)}\, , &
\label{e:aludvcs}
\end{align}
